---
title: "Diffusion"
author: "Gen Chiong, Quin Smith, Alex Vand"
date: "5/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Diffusion

```{r}
source("diffusion.R")
```



# Change parameters (diffusivity D, and space and time steps (dx, dt))

- initialC  initial concentration (mg/L)
- nx  number of discrete segments (m)
- dx length of each segment (m)
- nt  number of discrete time intervals (s)
- dt  seconds in each time interval (s)
- D  diffusivity (how easily the chemical diffuses (s/m2)
- area area of cross section of container (m2)


## "original"
```{r}
res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```


## initialC


```{r}
#original
#res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

#change initialC
res=diff1(initialC=100,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```


## nx


```{r}
#original
#res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

#change nx
res=diff1(initialC=10,nx=100,dx=1,nt=10,dt=1,D=0.5,area=1)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```


## dx

```{r}
#original
#res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

#change dx
res=diff1(initialC=10,nx=10,dx=10,nt=10,dt=1,D=0.5,area=1)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```



## nt


```{r}
#original
#res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

#change nt
res=diff1(initialC=10,nx=10,dx=1,nt=100,dt=1,D=0.5,area=1)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```



## dt


```{r}
#original
#res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

#change dt
res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=10,D=0.5,area=1)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```


## D


```{r}
#original
#res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

#change D
res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=5,area=1)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```


## area


```{r}
#original
#res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=1)

#change area
res=diff1(initialC=10,nx=10,dx=1,nt=10,dt=1,D=0.5,area=100)

filled.contour(res$conc, xlab="Time", ylab="Distance")

filled.contour(res$qin, xlab="Time", ylab="Distance")
```







